---
title: "Draft_1"
output: html_document
---

# Intro
Quick person
Background

I think will do accessing the data and analysing in seaborn in one, and then repeat in python.

# Accessing data
Tutorial to get data
```{python}

```



# Analysis in R

Import the packages we need
```{r}
library(ggplot2)
library(ggridges) # get rid of if don't use
library(dplyr)
library(plotly)
```

*Formatting the data*
First of all, we need to format the dataframe to a useable format.
```{r}
data <- read.csv("/Users/imytest/Library/Mobile Documents/com~apple~CloudDocs/Documents/Projects_for_fun/Strava/Data/Saves_from_API/21_Feb_11th.csv")
```

Now we are going to edit the start date local column, so that we have separate column for the year and month. 
```{r}
dates <- data.frame(do.call(
    "rbind",strsplit(as.character(data$start_date_local), "-", fixed = TRUE)))
data$year <- dates$X1
data$month <- dates$X2
# Then split that third column
month_df <- data.frame(do.call( "rbind", strsplit(as.character(dates$X3), " ", fixed = TRUE)))
data$day_number <- as.integer(month_df$X1)

# Is this needed?
#full_date <- data.frame(
#    do.call("rbind",strsplit(as.character(data_frame$start_date_local), " ", fixed=TRUE)))
#data$complete_date <- full_date$X1
```

Then, we're going to neaten up the days and months. Create a named column for each of the months, and order the days so that they plot in order.
```{r}
data$month_name <- with(dat, ifelse(
  month_of_year == 1 , 'January', ifelse(
  month_of_year == 2 , 'February', ifelse(
  month_of_year == 3 , 'March', ifelse(
  month_of_year == 4, 'April', ifelse(
  month_of_year == 5, 'May', ifelse(
  month_of_year == 6, 'June', ifelse(
  month_of_year == 7, 'July',ifelse(
  month_of_year == 8, 'August',ifelse(
  month_of_year == 9, 'September',ifelse(
  month_of_year == 10, 'October',ifelse(
  month_of_year == 11, 'November',ifelse(
  month_of_year == 12, 'December', NaN)))))))))))))
 
days <- c("Monday","Tuesday","Wednesday","Thursday","Friday","Saturday","Sunday")
data <- data %>% 
    mutate(day_of_week_str = factor(day_of_week, levels=days)) %>%
    mutate(c_distance_km=cumsum(distance_km))
```

Then, we are going to add string columns that convert the month number to a string (for neater plots)

```{r}
if (year_select/4 == 0){ # sort out how this interacts with the rest
    leap_days = 29
} else {
    leap_days = 28
}
data$month_days_since_jan01 <- with(data, ifelse(
  month_of_year == 1 , 0, ifelse(
  month_of_year == 2 , 31, ifelse(
  month_of_year == 3 , (leap_days+31), ifelse(
  month_of_year == 4, 91, ifelse(
  month_of_year == 5, 121, ifelse(
  month_of_year == 6, 152, ifelse(
  month_of_year == 7, 182,ifelse(
  month_of_year == 8, 213,ifelse(
  month_of_year == 9, 244,ifelse(
  month_of_year == 10, 274,ifelse(
  month_of_year == 11, 305,ifelse(
  month_of_year == 12, 335, NaN)))))))))))))
  
data$month_days_since_jan01 <- as.integer(data$month_days_since_jan01)
data$days_since_jan01 <- data$month_days_since_jan01 + data$day_number
data$month_days_since_jan01 <-NULL
  
data <- data %>% arrange(days_since_jan01) %>%
    mutate(distance_km_c = cumsum(distance_km)) # Potentially don't need this because of the cumsum on ggplot variable
  
  data_frame$X <- NULL
  data_frame$id <- NULL
  
  year_comparison <- as.character(year_select)
  data_frame <- data_frame[which(data_frame$year==year_comparison), ]
  
  return(data_frame)

```


*Plots*





# Analysis in python



