---
title: "Draft_1"
output: html_document
---

# Intro
Quick person
Background

# Accessing data
Tutorial to get data in python.a

# Analysis in R
Import the packages we need
```{r, return=False}
library(ggplot2)
library(plotly)
library(dplyr)
library(lubridate)
```

*Formatting the data*
First of all, we need to format the dataframe to a useable format.
```{r}
data <- read.csv("/Users/imytest/Library/Mobile Documents/com~apple~CloudDocs/Documents/Projects_for_fun/Strava/Data/Saves_from_API/21_Feb_11th.csv")
data$X <- NULL
data$id <- NULL
```

Now we are going to edit the start date local column, so that we have separate column for the year and month. Then, we're going to neaten up the days and months. Create a named column for each of the months, and order the days so that they plot in order.
```{r}
# Sorting out the date time column in datetime
data <- data %>% mutate(date = as.Date(start_date_local, "%Y-%m-%d"))
data$year <- year(data$date)
data$month <- month(data$date)
data$wday <- wday(data$date)
data$month_full <- month(data$date, label=TRUE)
data$wday_full <- wday(data$date, label=TRUE)
 # data$distance <- data$distance / 1000 # need to run in rea thing, but not now.
```

Then, we want to create our data frame of just 2020 data.
```{r}
twenty20 <- filter(data, year == 2020) # Create just this data frame
# Calculate time since beginning of year
baseline = as.Date("2020-01-01", "%Y-%m-%d")
twenty20$difference <- twenty20$date - baseline
twenty20 <- twenty20 %>% arrange(difference) 
twenty20$difference <- as.integer(twenty20$difference)
```

# First plot: Cumulative

First, lets see start with a basic cumulative plot, that shows how much I moved over time in the last year. Now we have that basic plot, we can go ahead and make it a plotly plot. ggplotly creates a wrapper around a ggplot to make it more interactive.
```{r}
baseplot <- ggplot(twenty20, aes(x = difference, y=cumsum(distance_km), color=type)) +
  geom_point() + # Line graph
  labs(x = 'Time', y = 'Distance', title ='Cumulative distance travelled over the year') + # Label the axes
  scale_x_continuous(breaks = seq(0,366,30)) + # Change tick marks x axis
  scale_y_continuous(breaks = seq(0,2800,200)) + # Change tick marks y axis
  theme_bw() # Remove grey background
baseplotly <- ggplotly(baseplot)
baseplotly
```

Great, now when I scroll over the line, I can see what activity contributed to the distance.
However, I want to be able to see the name of the activity - this evokes memories, and makes my strava data more interactive and memorable to me.
To do this, we need to add some information in to that baseplot, and the conversion to ggplotly.
The 'name' column is the one I want to analyse, so we add that in to the ggplot aesthetics. We then define the 'tooltip' in the ggplotly as using the name.
For this plot, I have converted to geom_point, so that I can colour the points by the activity type they are.

```{r}
ggplotly((ggplot(twenty20, aes(x = difference, y=cumsum(distance_km), color=type, text=name)) + 
  geom_point(group=1) + # Group=1 one needed to debug
  labs(x = 'Time', y = 'Distance') +
  # scale_color_discrete(name = "Activity") + 
  theme_bw()), 
  tooltip="text")
```

# Second plot: Time on each activity

Now we've gone through the steps of making a plotly ggplot once, we can make the rest quicker, and quickly get to look at our data. Next, I want to look at the amount of time I spent running and cycling over the year.

```{r}
# Recreate the columns in the python sheet for this - need to get the hours etc in minutes
#df$moving_time2 = pd.to_timedelta(df['moving_time'])
test <- data %>% mutate(date = as.Date(moving_time2, "%Y-%m-%d"))
#df$elapsed_time2  = pd.to_timedelta(df['elapsed_time']) 
a <- data$elapsed_time[][1]
data$elapsed_time2  = as.hms(data$elapsed_time,)
# Convert timings to hours for plotting
```


```{r}
ggplot(data) +
  geom_bar(aes(x=wday, y=moving_time_hr, fill = type), position = "dodge", stat="identity") +
  labs(x = 'Day', y = 'Time per activity') +
  theme_bw()

# Day since start of year against time
str(twenty20)

```

```{r}
ggplot(twenty20, aes(x=difference, y=elapsed_time_hr, color=type)) + geom_point() + facet_grid(type ~ .)
```




# Third plot
Finally, I'm going to look at just the running or cycling












