---
title: "Strava_analysis"
output: html_document
---
Analysis of the csv saved from Stravalib in jupyter.
Choosing RMarkdown at the moment, might recreate in seaborn to try it out.
```{r, return=FALSE}
library(ggplot2)
library(ggridges) # get rid of if don't use
library(dplyr)
library(plotly)
```

Import data.
```{r, return = FALSE}
data <- read.csv("/Users/imytest/Library/Mobile Documents/com~apple~CloudDocs/Documents/Projects_for_fun/Strava/Data/Saves_from_API/21_Feb_11th.csv")
```

Get data to a useable format.
Reorder the days of the week and order of activities. Split the 'start date' column up to year / month / day. 
```{r}
days <- c("Monday","Tuesday","Wednesday","Thursday","Friday","Saturday","Sunday")
type_order <- c("Ride","Run","Walk","Hike")
data <- data %>% 
  mutate(day_of_week_str = factor(day_of_week, levels=days)) %>%
  mutate(type_order = factor(type, levels=type_order)) %>%
  mutate(c_distance_km=cumsum(distance_km))
date <- data.frame(do.call("rbind", strsplit(as.character(data$start_date_local), "-", fixed = TRUE)))
month <- data.frame(do.call("rbind", strsplit(as.character(date$X3), " ", fixed = TRUE)))
full_date <- data.frame(do.call("rbind", strsplit(as.character(data$start_date_local), " ", fixed = TRUE)))
# Need to sort out these so they would make sense to someone else. 
# Possibly do it from one string split?
data$year <- date$X1
data$month <- date$X2
data$full_date <- full_date$X1
data$day <- month$X1
twenty20 <- data[which(data$year=='2020'), ]
colnames(twenty20)
```


Add the months by name, and calculate the number of days since the beginning of the year for each month, leading to each activity. Add column of cumulative distance travelled.
```{r}
twenty20 <- twenty20
twenty20$month_name <- with(twenty20, ifelse(
  month_of_year == 1 , 'January', ifelse(
  month_of_year == 2 , 'February', ifelse(
  month_of_year == 3 , 'March', ifelse(
  month_of_year == 4, 'April', ifelse(
  month_of_year == 5, 'May', ifelse(
  month_of_year == 6, 'June', ifelse(
  month_of_year == 7, 'July',ifelse(
  month_of_year == 8, 'August',ifelse(
  month_of_year == 9, 'September',ifelse(
  month_of_year == 10, 'October',ifelse(
  month_of_year == 11, 'November',ifelse(
  month_of_year == 12, 'December','NOT YET')))))))))))))

twenty20$month_days_since_jan01 <- with(twenty20, ifelse(
  month_of_year == 1 , 0, ifelse(
  month_of_year == 2 , 31, ifelse(
  month_of_year == 3 , 60, ifelse( # leap year
  month_of_year == 4, 91, ifelse(
  month_of_year == 5, 121, ifelse(
  month_of_year == 6, 152, ifelse(
  month_of_year == 7, 182,ifelse(
  month_of_year == 8, 213,ifelse(
  month_of_year == 9, 244,ifelse(
  month_of_year == 10, 274,ifelse(
  month_of_year == 11, 305,ifelse(
  month_of_year == 12, 335,'NO')))))))))))))

twenty20$day <- as.integer(twenty20$day)
twenty20$month_days_since_jan01 <- as.integer(twenty20$month_days_since_jan01)
twenty20$days_since_jan01 <- twenty20$month_days_since_jan01 + twenty20$day

twenty20 <- twenty20 %>% 
  arrange(days_since_jan01) %>%
  mutate(distance_km_c = cumsum(distance_km))
```

# ggplots

Overall view of activities. 

```{r}
# Improve from days of the week to better metric
overall_plot <- ggplot(twenty20, aes(x = day_of_week_str, y=distance_km, color=month_of_year)) + 
  geom_point() +
  labs(x = 'Activity', y = 'Distance') +
  facet_grid(. ~ type) +
  theme(axis.text.x = element_text(angle = 90))
overall_plot
```

Plot of how much each activity has contributed to the overall distance travelled.
```{r}
total <- ggplot(twenty20, aes(x=days_since_jan01, y=distance_km_c, color=type)) +
  geom_point() + 
  theme_bw() + facet_grid(. ~ type) + labs(x="Days since beginning of year", y="Cumulative distance (km)")
total
```

# Plotly interactive plots

Need to try and integrate with ggplot -> think it will make sense https://plotly.com/ggplot2/cumulative-animations/

```{r}
distance <- plot_ly(data, x = ~distance_km, color = ~type, type = "box")
distance
```

```{r}
fig <- plot_ly(twenty20, x = ~distance_km, y=~day_of_week_str, trace="bar")
fig
```

# Traditional ggplot
Initial plots that need refining








## Ridge plots of activity over time
Work in progress
```{r}
ggplot(twenty20, aes(x = day, y = month_of_year)) +
  geom_density_ridges(scale = 1) + 
  scale_y_discrete(expand = c(0, 0)) +     # will generally have to set the `expand` option
  scale_x_continuous(expand = c(0, 0)) +   # for both axes to remove unneeded padding
  coord_cartesian(clip = "off") + # to avoid clipping of the very top of the top ridgeline
  theme_ridges()
```

