---
title: "Strava_analysis"
output: html_document
---
Analysis of the csv saved from Stravalib in jupyter.
Choosing RMarkdown at the moment, might recreate in seaborn to try it out.
```{r, return=FALSE}
library(ggplot2)
library(ggridges) # get rid of if don't use
library(dplyr)
library(plotly)
```

Import data.
```{r, return = FALSE}
data <- read.csv("/Users/imytest/Library/Mobile Documents/com~apple~CloudDocs/Documents/Projects_for_fun/Strava/Data/Saves_from_API/21_Feb_11th.csv")
```

Get data to a useable format.
Reorder the days of the week and order of activities. Split the 'start date' column up to year / month / day. Want to be able to format per year --> needs to be a function.
Add the months by name, and calculate the number of days since the beginning of the year for each month, leading to each activity. Add column of cumulative distance travelled.
For the post, can just do it linearly and edit to each year as I go.
```{r}
data_setup <- function(data_frame, year_select){
  
    date_df <- data.frame(do.call(
    "rbind",strsplit(as.character(data_frame$start_date_local), "-", fixed = TRUE)))
  data_frame$year <- date_df$X1
  data_frame$month <- date_df$X2
 
  days <- c("Monday","Tuesday","Wednesday","Thursday","Friday","Saturday","Sunday")
  data_frame <- data_frame %>% 
    mutate(day_of_week_str = factor(day_of_week, levels=days)) %>%
    mutate(c_distance_km=cumsum(distance_km))
  
  full_date <- data.frame(
    do.call("rbind",strsplit(as.character(data_frame$start_date_local), " ", fixed=TRUE)))
  data_frame$complete_date <- full_date$X1
  
  month <- data.frame(do.call( "rbind", strsplit(as.character(date_df$X3), " ", fixed = TRUE)))
  data_frame$day_number <- as.integer(month$X1)
  
  if (year_select/4 == 0){
    leap_days = 29
  } else {
    leap_days = 28
  }
  
  data_frame$month_name <- with(data_frame, ifelse(
  month_of_year == 1 , 'January', ifelse(
  month_of_year == 2 , 'February', ifelse(
  month_of_year == 3 , 'March', ifelse(
  month_of_year == 4, 'April', ifelse(
  month_of_year == 5, 'May', ifelse(
  month_of_year == 6, 'June', ifelse(
  month_of_year == 7, 'July',ifelse(
  month_of_year == 8, 'August',ifelse(
  month_of_year == 9, 'September',ifelse(
  month_of_year == 10, 'October',ifelse(
  month_of_year == 11, 'November',ifelse(
  month_of_year == 12, 'December', NaN)))))))))))))

  data_frame$month_days_since_jan01 <- with(data_frame, ifelse(
  month_of_year == 1 , 0, ifelse(
  month_of_year == 2 , 31, ifelse(
  month_of_year == 3 , (leap_days+31), ifelse(
  month_of_year == 4, 91, ifelse(
  month_of_year == 5, 121, ifelse(
  month_of_year == 6, 152, ifelse(
  month_of_year == 7, 182,ifelse(
  month_of_year == 8, 213,ifelse(
  month_of_year == 9, 244,ifelse(
  month_of_year == 10, 274,ifelse(
  month_of_year == 11, 305,ifelse(
  month_of_year == 12, 335, NaN)))))))))))))
  
  data_frame$month_days_since_jan01 <- as.integer(data_frame$month_days_since_jan01)
  data_frame$days_since_jan01 <- data_frame$month_days_since_jan01 + data_frame$day_number
  data_frame$month_days_since_jan01 <-NULL
  
  data_frame <- data_frame %>% 
    arrange(days_since_jan01) %>%
    mutate(distance_km_c = cumsum(distance_km)) # Potentially don't need this because of the cumsum on ggplot variable
  
  data_frame$X <- NULL
  data_frame$id <- NULL
  
  year_comparison <- as.character(year_select)
  data_frame <- data_frame[which(data_frame$year==year_comparison), ]
  
  return(data_frame)
}
```

```{r}
twenty19 <- data_setup(data_frame = data, year_select = 2019)
twenty20 <- data_setup(data_frame = data, year_select = 2020)
twenty21 <- data_setup(data_frame = data, year_select = 2021)
```

# ggplots

```{r}
colnames(twenty20)
```

Overall view of activities
```{r}
cumulative_distance_line <- ggplot(twenty20, aes(x = days_since_jan01, y=distance_km_c)) + geom_line() +
  labs(x = 'Activity', y = 'Distance') +
  scale_color_discrete(name = "Activity") +
  scale_x_continuous(breaks = seq(0,366,30)) +
  scale_y_continuous(breaks = seq(0,2800,200)) +
  theme_bw()
cumulative_distance_line_plotly <- ggplotly(cumulative_distance_line)
cumulative_distance_line_plotly
```

```{r}
cumulative_distance_line <- ggplot(twenty21, aes(x = days_since_jan01, y=distance_km_c)) + geom_line() +
  labs(x = 'Activity', y = 'Distance') +
  scale_color_discrete(name = "Activity") +
  scale_x_continuous(breaks = seq(0,366,30)) +
  scale_y_continuous(breaks = seq(0,250,50)) + 
  theme_bw() +
  geom_abline(slope = (2500/365), aes(colour='blue'))
cumulative_distance_line_plotly <- ggplotly(cumulative_distance_line)
cumulative_distance_line_plotly
```


```{r}
cumulative_distance <- ggplot(twenty20, aes(x = days_since_jan01, y=distance_km_c, color=type)) + 
  geom_point() +
  labs(x = 'Activity', y = 'Distance') +
  scale_color_discrete(name = "Activity") + 
  theme_bw()
cumulative_distance_plotly <- ggplotly(cumulative_distance)
cumulative_distance_plotly
```

Plot of how much each activity has contributed to the overall distance travelled.
```{r}
total <- ggplot(twenty20, aes(x=days_since_jan01, y=distance_km, color=type)) +
  geom_point() + 
  theme_bw() + facet_grid(. ~ type) + labs(x="Days since beginning of year", y="Distance (km)") + 
  # scale_x_continuous(limits = c(0, 120)) +
  scale_y_continuous(breaks = seq(0,130,10))
total_plotly <- ggplotly(total)
total_plotly
```

# Cycling
Look at only cycling activities.
```{r}
cycle <- twenty20[which(twenty20$type=='Ride'), ] # only 2020 atm, remake for the real thing
dim(cycle)
```

```{r}
cyc_distance <- ggplot(cycle, aes(x = days_since_jan01, y=cumsum(distance_km), color=day_of_week, text = name)) + 
  geom_point() +
  labs(x = 'Activity', y = 'Cumulative distance') +
  scale_color_discrete(name = "Day") + 
  theme_bw() +
  scale_y_continuous(breaks = seq(0,2500,200))
ggplotly(cyc_distance, tooltip = "text")
```

```{r}
cyc_hist <- ggplot(cycle, aes(x = max_heartrate)) + 
  geom_histogram() +
  labs(x = 'Activity', y = 'Cumulative distance') +
  scale_color_discrete(name = "Day") + 
  theme_bw() +
  scale_y_continuous(breaks = seq(0,2500,200))
ggplotly(cyc_hist)
```

## Ridge plots of activity over time
Work in progress
```{r}
ggplot(twenty20, aes(x = day, y = month_of_year)) +
  geom_density_ridges(scale = 1) + 
  scale_y_discrete(expand = c(0, 0)) +     # will generally have to set the `expand` option
  scale_x_continuous(expand = c(0, 0)) +   # for both axes to remove unneeded padding
  coord_cartesian(clip = "off") + # to avoid clipping of the very top of the top ridgeline
  theme_ridges()
```

