---
title: "Strava_analysis"
output: html_document
---

Analysis of the csv saved from Stravalib in jupyter.
Choosing RMarkdown at the moment, might recreate in seaborn to try it out.
```{r, return=FALSE}
library(ggplot2)
library(ggridges)
library(dplyr)
library(plotly)
#install.packages("ggridges")
#install.packages("dplyr")
```

```{r, return = FALSE}
data <- read.csv("/Users/imytest/Library/Mobile Documents/com~apple~CloudDocs/Documents/Projects_for_fun/Strava/Data/Saves_from_API/21_Feb_11th.csv")
colnames(data)
# data$type <- factor(data$type, levels = sort(levels(data$value))) # Refactoring the order of activities
```
Sorting out the original data frame
```{r}
summary(data)
# refactor 'type'
data <- data %>% mutate(day_of_week_str = fct_relevel(day_of_week,
            ))
days =c("Monday","Tuesday","Wednesday","Thursday","Friday","Saturday","Sunday")
data <- data %>% 
  mutate(day_of_week_str = factor(day_of_week,levels=days))
twenty20 <- twenty20 %>% 
  mutate(day_of_week_str = factor(day_of_week,levels=days))
# refactor 'day_of_week'
# add column on month by name 
head(data)
```
# Learning plotly

```{r}
# fig <- plot_ly(data, x = ~percollege, color = ~state, type = "box")
fig <- plot_ly(data, x = ~distance_km, color = ~type, type = "box")
fig
```

```{r}
fig <- plot_ly(twenty20, x = ~distance_km, y=~day_of_week_str, trace="bar")
fig
```




# Traditional ggplot
Initial plots that need refining

```{r}
#test = str_split(data$start_date_local, "-", n = 1)
date <- data.frame(do.call("rbind", strsplit(as.character(data$start_date_local), "-", fixed = TRUE)))
data$year <- date$X1

twenty20 <- data[which(data$year=='2020'), ]
colnames(twenty20)
```











```{r}
ggplot(data, aes(x = type, y=distance_km, color = type)) + 
  geom_boxplot() +
  labs(x = 'Activity', y = 'Distance') +
  facet_grid(. ~ day_of_week_str) +
  theme(axis.text.x = element_text(angle = 90))
```


```{r}
ggplot(data, aes(x = max_heartrate, y=distance_km)) + 
  geom_point() +
  labs(x = 'Max heartrate', y = 'Distance')
```

```{r}
ggplot(data, aes(x = elapsed_time_hr, y= distance_km)) + 
  geom_point() +
  labs(x = 'Max heartrate', y = 'Distance')
```


*PLOTS TO MAKE:*
Start latitude / londitude
Start plotting a map of start longitude / latitude
Cumulative distance over time
Max speed by activity.
Want to do some kind of ridge plot.
Then integrate to plotly.


## Ridge plots of activity over time
Work in progress
```{r}
ggplot(data = twenty20, aes(x = start_date_local, y = month_of_year, group = month_of_year, height=max_heartrate)) +
  geom_density_ridges(stat="identity", scale=1) +
  theme_ridges() + 
  theme(legend.position = "none")
```

